Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
added DOI and reduce space
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
typo

\CopyrightYear{2017}
\setcopyright{acmcopyright}
\conferenceinfo{HSCC '17,}{April 18--20, 2017, Pittsburgh, PA, USA.}
\isbn{978-1-4503-4590-3/17/04}\acmPrice{\$15.00.}
\doi{TBD.}

@@

Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Springer-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}). The uncertainties are deviations bounded to a maximum magnitude of $0.5$ in each coefficient. These uncertain models are respectively represented by $G_{1b}(z)$, $G_{2b}(z)$, $G_{3b}(z)$, and $G_{3d}(z)$.

>>>>

\CopyrightYear{2017}
\setcopyright{rightsretained}
\conferenceinfo{HSCC '17,}{April 18--20, 2017, Pittsburgh, PA, USA.}
\isbn{978-1-4503-4590-3/17/04}%\acmPrice{\$15.00.}
\doi{http://dx.doi.org/10.1145/3049797.3049802}

@@

Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Spring-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}). The uncertainties are deviations bounded to a maximum magnitude of $0.5$ in each coefficient. These uncertain models are respectively represented by $G_{1b}(z)$, $G_{2b}(z)$, $G_{3b}(z)$, and $G_{3d}(z)$.
